NMRlipids IV: Headgroup \& glycerol backbone structures, and cation binding in bilayers with PS lipids

### 2018-03-27 Manuscript/manuscriptPS.tex
Add Berger results as a function of monovalent ions plotted with experimental data delivered in previous commit https://github.com/NMRLipids/NMRlipidsIVotherHGs/commit/b93473d40004729f0b8d0346a362ba9594fc8008

In order to compare the sodium interaction with PS containing membranes between
experiments and simulations, Fig. \ref{PSresponseTONaCl} shows the order parameters of the
$\alpha$ carbon of PS headgroup measured from the mixture with PC as a
function of added NaCl \cite{roux86} together with the resuls from CHARMM36 model. 
\begin{figure}[]
  \centering
  \includegraphics[width=9.0cm]{../Figs/PSresponseTONaCl.eps}
  \caption{\label{PSresponseTONaCl}
    Order parameters of PS headgroup as a function of added NaCl measured from DMPC:DMPS (3:1) mixture \cite{roux86}.
  }
\end{figure}
The experimental results show essentially no changes in the order parameters as a function of
added NaCl, while significant changes are observed in simulations. However,
the minimum buffer concentration of NaCl in the experimental was 100mM \cite{roux86}.
Therefore, we cannot exclude the possibility that the NaCl induced changes were already
saturated with 100mM NaCl concentration, which was the case for CaCl$_2$ in Fig. \ref{changesWITHCaClPS}.
\todo{It would be probably better to use datasets for NaCl and KCl from Ref. \citenum{roux90}
to compare monovalent ion binding to PS containing bilayer.}

@@

>>>>

In order to compare the sodium interaction with PS containing membranes between
experiments and simulations, Fig. \ref{PSresponseTONaCl} shows the order parameters of the
$\alpha$ carbon of PS headgroup measured from the mixture with PC as a
function of added NaCl \cite{roux86} together with the resuls from CHARMM36 model. 
\begin{figure*}[]
  \centering
  \includegraphics[width=18.0cm]{../Figs/CHANGESwithMONVALENTwithPS.eps}
  \caption{\label{PSresponseTONaCl}
    Order parameters of PC (left) and PS (right) headgroup as a function of added NaCl measured from POPC:POPS (5:1) mixture \cite{roux90}.
  }
\end{figure*}
The experimental results show essentially no changes in the order parameters as a function of
added NaCl, while significant changes are observed in simulations. However,
the minimum buffer concentration of NaCl in the experimental was 100mM \cite{roux86}.
Therefore, we cannot exclude the possibility that the NaCl induced changes were already
saturated with 100mM NaCl concentration, which was the case for CaCl$_2$ in Fig. \ref{changesWITHCaClPS}.
\todo{It would be probably better to use datasets for NaCl and KCl from Ref. \citenum{roux90}
to compare monovalent ion binding to PS containing bilayer.}

@@

\begin{figure}[]
  \centering
  \includegraphics[width=9.0cm]{../Figs/PSresponseTONaCl.eps}
  \caption{\label{PSresponseTONaCl}
    Order parameters of PS headgroup as a function of added NaCl measured from DMPC:DMPS (3:1) mixture \cite{roux86}.
  }
\end{figure}
